|

### 2025-01-20 doc/paper.qmd
added list of tables and figures (for better navigation)

bibliography: references.bib
biblio-style: apsr
format:
  pdf:
    documentclass: article
    number-sections: true
    toc: true
fig_caption: yes
fontsize: 11pt
ident: yes
always_allow_html: yes
number-sections: true 
header-includes:
  - \usepackage[nolists]{endfloat}    
  - \usepackage{setspace}\doublespacing
  - \setlength{\parindent}{4em}
  - \setlength{\parskip}{0em}
  - \usepackage[hang,flushmargin]{footmisc}
  - \usepackage{caption} 
  - \captionsetup[table]{skip=24pt,font=bf}
  - \usepackage{array}
  - \usepackage{threeparttable}
  - \usepackage{adjustbox}
  - \usepackage{graphicx}
  - \usepackage{csquotes}
  - \usepackage{indentfirst}  # Added this line to ensure the first paragraph is indented for better readability
  - \usepackage[margin=1in]{geometry}
---

@@

# List of Abbreviations
\setlength{\parindent}{0em}
**CRSP**: Center for Research in Security Prices
**EC**: European Commission  
**EU**: European Union  
**IDE**: Integrated Development Environment  
**NCA**: National Competent Authority  
**PIE**: Public interest entity  
**TREAT**: TRR 266 Template for Reproducible Empirical Accounting Research  
**UK**: United Kingdom   
**WRDS**: Wharton Research Data Services

>>>>

bibliography: references.bib
biblio-style: apsr
format:
  pdf:
    documentclass: article
    number-sections: true
    toc: true
    lof: true  # Enables List of Figures
    lot: true  # Enables List of Tables
fig_caption: yes
fontsize: 11pt
ident: yes
always_allow_html: yes
number-sections: true 
header-includes:
  - \usepackage[nolists]{endfloat}    
  - \usepackage{setspace}\doublespacing
  - \setlength{\parindent}{4em}
  - \setlength{\parskip}{0em}
  - \usepackage[hang,flushmargin]{footmisc}
  - \usepackage{caption} 
  - \captionsetup[table]{skip=24pt,font=bf}
  - \usepackage{array}
  - \usepackage{threeparttable}
  - \usepackage{adjustbox}
  - \usepackage{graphicx}
  - \usepackage{csquotes}
  - \usepackage{indentfirst}  # Added this line to ensure the first paragraph is indented for better readability
  - \usepackage[margin=1in]{geometry}
---

@@

# List of Abbreviations
\setlength{\parindent}{0em}
**CRSP**: Center for Research in Security Prices
**EC**: European Commission  
**EU**: European Union  
**IDE**: Integrated Development Environment  
**TREAT**: TRR 266 Template for Reproducible Empirical Accounting Research  
**UK**: United Kingdom   
**WRDS**: Wharton Research Data Services
